### 2018-09-12 doc/plos/text/manuscript.tex
correction for number of sensors

Our estimate of the covariance of sensor ``noise'' (residuals w.r.t. ground
truth) $R$ is necessarily imperfect. Adding additional sensors exponentially
increases the dimension of the problem without adding new observations---the
curse of dimensionality. With 367 sensor-location pairs, $R$ has shape $367
\times 376$; yet in the best case we only have a few hundred observations from
which to estimate this covariance---often much fewer. Our only recourse is
aggressive regularization at the expense of covariance accuracy, and therefore
nowcast accuracy.

>>>>

Our estimate of the covariance of sensor ``noise'' (residuals w.r.t. ground
truth) $R$ is necessarily imperfect. Adding additional sensors exponentially
increases the dimension of the problem without adding new observations---the
curse of dimensionality. With up to 363 sensor-location pairs, $R$ has shape
$363 \times 363$; yet in the best case we only have a few hundred observations
from which to estimate this covariance---often much fewer. Our only recourse is
aggressive regularization at the expense of covariance accuracy, and therefore
nowcast accuracy.
